---
output: rmarkdown::github_document
---

`voteogram` : U.S. House and Senate Voting Cartogram Generators

Produce voting cartograms in the style of 'ProPublica'.

Ref: <https://projects.propublica.org/represent/votes/115/senate/1/110>

### TODO

- House cartogram generator
- `htmlwidget` version
- Colors for "not voting" & "present"
- Carto theme
- Ability to retrieve votes from ProPublica.

The following functions are implemented:

- `senate_carto`: Produce a Senate cartogram

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/voteogram")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(voteogram)
library(jsonlite)
library(hrbrthemes)
library(tidyverse)

# current verison
packageVersion("voteogram")
```

```{r cache=TRUE}
df <- fromJSON("https://pp-projects-static.s3.amazonaws.com/congress/assets/senate_115_1_110.json")$votes
```

```{r fig.width=10, fig.height=7}
select(df, state_abbrev, district, party, position) %>% 
  senate_carto() +
  labs(title="Senate Vote 110 - Invokes Cloture on Neil Gorsuch Nomination") +
  theme_ipsum_rc(grid="", plot_title_size = 24) +
  theme(axis.text=element_blank())
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(voteogram)
library(testthat)

date()

test_dir("tests/")
```

