---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r include=FALSE}
knitr::opts_chunk$set(fig.retina=2)
```
`voteogram` : U.S. House and Senate Voting Cartogram Generators

Produce voting cartograms in the style of 'ProPublica'.

Ref: <https://projects.propublica.org/represent/votes/115/senate/1/110>

### TODO

- <strike>House cartogram generator</strike>
- `htmlwidget` version
- Colors for <strike>"vacant"</strike>, not voting" & "present"
- Make a `voteogram` theme
- <strike>Param bulletproofing (param checking, et al)</strike>
- <strike>Add in ability to retrieve votes from ProPublica.</strike>

The following functions are implemented:

- `house_carto`:	Produce a House cartogram
- `print.pprc`:	Better default 'print' function for `roll_call()` (`pprc`) objects
- `roll_call`:	Get Voting Record for House or Senate By Number, Session & Roll Call Number
- `senate_carto`:	Produce a Senate cartogram

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/voteogram")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(voteogram)
library(jsonlite)
library(hrbrthemes)
library(tidyverse)

# current verison
packageVersion("voteogram")
```

```{r cache=TRUE}
sen <- roll_call("senate", 115, 1, 110)
rep <- roll_call("house", 115, 1, 256)
```

```{r}
sen

sen$votes
```

```{r}
rep

rep$votes
```

```{r sen, fig.width=10, fig.height=7}
senate_carto(sen) +
  labs(title="Senate Vote 110 - Invokes Cloture on Neil Gorsuch Nomination") +
  theme_ipsum_rc(grid="", plot_title_size = 24) +
  theme(axis.text=element_blank())
```

```{r rep, fig.width=10, fig.height=7}
house_carto(rep) +
  labs(title="House Vote 256 - Passes American Health Care Act,\nRepealing Obamacare") +
  theme_ipsum_rc(grid="", plot_title_size = 24) +
  theme(axis.text=element_blank())
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(voteogram)
library(testthat)

date()

test_dir("tests/")
```

